---
title: "Test Package with Spotifyr DataSet"
output: html_notebook
---
Our goal is to perform different clustering methods on tracks from several artist.\
I selected ... but if you set up the [spotifyr](https://www.rcharlie.com/spotifyr/) package, like described below, feel free to try out the clustering methods for other artists as well.

If not you can skip directly to the second part of part 2.

The data we will look at contains information about the

- **danceability** (number between zero and one)
- **energy** (number between zero and one)
- **acousticness**
- **duration_ms** (duration in ms)
- **loudness**
- **tempo**
- **instrumentalness** 

# Import Data Set
### 1. Set up spotifyr
Set up spotifyr like described [here](https://www.rcharlie.com/spotifyr/)
```{r}
library(spotifyr)
Sys.setenv(SPOTIFY_CLIENT_ID = 'xxxxxxxxxxxxxxxxxxxxx')
Sys.setenv(SPOTIFY_CLIENT_SECRET = 'xxxxxxxxxxxxxxxxxxxxx')

access_token <- get_spotify_access_token()
```

### 2. Get the artist data
Import the data and apply some data tidying
```{r}
beatles <- get_artist_audio_features('the beatles')

beatles %>% 
  select(danceability, energy, acousticness, duration_ms, loudness, tempo, instrumentalness) %>% 
  drop_na() -> beatles
```
Or simply import it from the .csv file
```{r}
library(readr)
beatles <- read_csv(beatles.csv)
```

# Apply various clustering methods
## Original Data 
```{r}
beatles %>% 
  arrange(danceability) %>% 
  head(100) %>% 
  select(duration_ms, tempo, energy) -> data
plot(data)
```
## KMeans
```{r}
kMeans <- new_kMeans(data = data, k=2)
plot_cluster(kMeans)
```
## KMedoids
```{r}
kMedoids <- kmedoid(data = data, k=2, iter=20)
plot_cluster(kMedoids)
```
## Hierarchichal
```{r}
data <- as.matrix(data)
hierarchical <- agglomerative_hierarchical_clustering(data = data, K=2, linkage_fun = "single")
plot_cluster(hierarchical)
```

## Spectral
### KMeans
```{r}
spectral <- spectral_clustering(data,
                              num_clusters=3,
                              dim_k=2,
                              cluster_fun=new_kMeans,
                              arg_cluster_fun = list(type="kMeans"))
plot_cluster(spectral)
```
### KMediods
```{r}
spectral <- spectral_clustering(data,
                              num_clusters=3,
                              dim_k=2,
                              cluster_fun=kmedoid)
plot_cluster(spectral)
```
### Hierarchical
```{r}
spectral <- spectral_clustering(data[, c(1,3) ],
                              num_clusters=3,
                              dim_k=2,
                              cluster_fun=agglomerative_hierarchical_clustering,
                              arg_cluster_fun = list(linkage_fun="single"))
plot_cluster(spectral)
```
